	In this section we study the globally almost surely asymptotic stability (as-stability) of the 
Linear Steklov  method \crefrange{eqn:SSLSM1}{eqn:SSLSM2}, in the scalar case.
For simplicity we assume that
$$
	f(x) = a(x)x,
$$
for some suitable nonlinear function $a:\R \to \R$.
Here, we will follow the same technique reported by \citeauthor*{Mao2013} in \cite{Mao2013}.
First, we need sufficient conditions to characterize when the solution of the SDE \eqref{eqn:SDE1} is as-stable. 
The following result deals with it.

\begin{thm}[Mao and Szpruch {\cite[Thm. 2.2]{Mao2013}}]
	Let \cref{ass:OSLC} hold and suppose that there exist a function $z\in \mathcal{C}(\mathbb{R}^d,\mathbb{R}_+)$
	such that
	\begin{equation*}
		\innerprod{x}{f(x)} +
		\frac{1}{2}|g(x)|^2\leq -z(x), \qquad \forall x\in \mathbb{R}^d,
	\end{equation*}
	then 
	\begin{enumerate}[(i)]
		\item
			For any $y_0\in \mathbb{R}^n$ the solution of the SDE \eqref{eqn:SDE1}, $y(t)$, satisfies
			\begin{equation*}
				\limsup_{t\to \infty}
					|y(t)|^2 \leq \infty \qquad \as \qquad \text{and} \qquad 
					\lim_{t\to \infty} z(y(t))= 0 \qquad \as
			\end{equation*}
		\item
			additionally, if $z(x)=0$ only when it is evaluated at $x=0$, then
			\begin{equation*}
				\lim_{t\to \infty} y(t)=0 \qquad \as \qquad \forall y_0\in \R^d.
			\end{equation*}
	\end{enumerate}
\end{thm}

	Next, %in\Cref{thm:AlmosSurleyStability}
we prove that \SM method emulates the as-stability.
The proof of this result hinges on the \Cref{lem:MartingaleConvergence} see for instance 
\cite[Th. 7, pg. 139]{Liptser1989}.
We will denote by  $\{Z\to\}$ the set of all $\omega \in \Omega$ for which the scalar process $Z$ has the property that
$\lim_{k\to\infty} Z_k$ exists and is finite.
\begin{lem}[{\cite[Thm. 7, pg. 139]{Liptser1989}}]
	\label{lem:MartingaleConvergence}
	Let $Z= \{Z_k\}$ be a nonnegative semimartingale with $\mathbb{E}|Z|<\infty$ and Doob decomposition 
	$$
		Z = Z_0 + A^{(1)} -A^{(2)} + M,
	$$
	where 
	$A^{(1)}:=\{A_k^{(1)}\}_{k\in \N}$ and $A^{(2)}:=\{A_k^{(2)}\}_{k\in \N}$ are $\as$ nondecreasing predictable
	processes with $A_0^{(1)}=A_0^{(2)}=0$ and $M:=\{M_k\}_{k\in\N}$ is a local $\{\calF_k\}$-martingale with $M_0=0$.
	Then
	\begin{equation*}
		\left\{
			%\omega:
			%\lim_{n\to \infty}
				A^{(1)} \to
		\right\}
		\subseteq
		\left\{
			%\omega:
			%\lim_{n\to \infty}
				A^{(2)} \to
		\right\}\cap
		\left\{
			%\lim_{n\to \infty}
			Z \to
		\right\} \qquad \as
\end{equation*}
\end{lem}
\begin{thm}\label{thm:AlmosSurleyStability}
		Let \Cref{ass:OSLC} holds. Suppose that there is a function 
		$z \in \calC(\R^n,\R_+)$ 
		and a step size $h^*>0$ such that for all $x\in \R$ and for all $h$ in $(0,h^*)$,
		\begin{align} 
			\innerprod{x}{f(x)} + \frac{1}{2}|g(x)|^2
			&\leq -z(x), \label{eqn:ConditionStability1}\\
			|x|^2
			\frac{(\exp(2 h a(x))-1)}{h}
			+|g_h(x)|^2
			&\leq
				-z(x), \label{eqn:ConditionStability2}
		\end{align}
	Then the \SM method defined by \crefrange{eqn:SSLSM1}{eqn:SSLSM2} satisfies
	\begin{align*}
		\limsup_{k\to \infty}
			|Y_k|^2 
			& <\infty \quad\text{ and} 
			\quad
		\lim_{k\to \infty}
			w(Y_k) =0. 
	\end{align*}
In addition, if $z(x)=0$ only when $x=0$, then
	$ \displaystyle
		\lim_{k\to \infty} Y_k = 0.
	$
\end{thm}
\begin{proof}
	Taking advantage of \Cref{lem:MartingaleConvergence}, we proceed to construct a conveniently 
	semimartingale. To
	\begin{align}
		|Y_{k+1}|^2
			&=
				|Y_{k}|^2
				+h^2|\varphi_{f_h}(Y_{k})|^2 
				+|g_h(Y_k) \Delta W_k|^2 \notag 
				+2h\innerprod{Y_k}{\varphi_{f_h}(Y_{k})} 
				\notag\\
			%
			&
				+2\innerprod{Y_k}{g_h(Y_{k})\Delta W_k}
				+2h\innerprod{\varphi_{f_h}(Y_{k})}{g_h(Y_{k})\Delta W_k}.
			\label{eqn:ExpandOfYnext}
	\end{align}
	Let 
	\begin{align*}
		\Delta M_{k+1}
			&:=
				|g_h(Y_k)\Delta W_{k+1}|^2 - |g_h(Y_k)|^2 h \notag \\
			&
			+2\innerprod{Y_k}{g_h(Y_{k})\Delta W_{k+1}}
			+2h\innerprod{\varphi_{f_h}(Y_{k})}{g_h(Y_{k})\Delta W_{k+1}}, \notag
	\end{align*}
	which is a local martingale.
	Taking
	$ %\begin{equation}\label{eqn:BjNotation}
		B_j:=
			-\left[
					2\innerprod{Y_j}{\varphi_{f_h}(Y_j)}
					+|g_h(Y_j)|^2
				+h|\varphi_{f_h}(Y_j)|^2
			\right],
	$ %\end{equation}
	and fixing $N\in \N$, we can rewrite \eqref{eqn:ExpandOfYnext} as
	\begin{align}\label{eqn:MartingaleDecomposition}
		|Y_{N+1}|^2 = 
			|Y_0|^2
				-\sum_{j=0}^{N} B_j h
				+\sum_{j=0}^{N} \Delta M_{j+1}.
	\end{align} 
	To prove that \eqref{eqn:MartingaleDecomposition} is the required decomposition to apply
	\Cref{lem:MartingaleConvergence}, we use that
	\begin{equation}\label{eqn:varphih(x)}
		\varphi_{f_h}(x)
			= x\frac{\left(\exp(h a(x))-1\right)}{h}.
	\end{equation}
	By algebraic manipulations, we obtain
	\begin{equation*}
		B_j=
		-\left[
			|Y_j|^2\frac{(\exp(2h a(Y_j))-1)}{h}
			+|g_h(Y_j)|^2
		\right],
		%\geq z(Y_j) \geq 0,
		\qquad
		 j=0,\dots,N.
	\end{equation*}
	Given that the inequality \eqref{eqn:ConditionStability2} holds, we can deduce that
	$$
		B_j\geq z(Y_j) \geq 0, \quad j=0,\ldots N.
	$$
	Consequently, $A_k^{(2)}:=\sum_{j=0}^k B_jh$ is a non decreasing process.
	Finally, taking $A^{(1)}=0$,  $Z=|Y_k|^2$ and $M_k=\sum_{j=0}^k \Delta M_{j+1}$.
	We can deduce  by \Cref{lem:MartingaleConvergence} that $\{A^{(1)}\to\}=\Omega$, thus
	\begin{align*}
	 \limsup_{k\to \infty}
			|Y_k|^2 < \infty \quad \as,
		\quad \text{and} \quad
		\sum_{j=0}^\infty z(Y_k) 
		\leq 
		\sum_{j=0}^\infty B_jh < \infty.
	\end{align*}
	Consequently
	$
		%\displaystyle
		\lim_{k\to \infty} z(Y_k) =0
	$,
	and the theorem follows.
	$\square$
\end{proof}
%
