In this work we have extended the explicit Steklov scheme for 
vector SDE by developing a new version  based on a 
linearized Steklov average. This method is 
constructed on the basis that the drift function 
can be rewritten  in the linearized form. 
Moreover, strong order one-half convergence has been proved for our explicit 
linear method and we have presented  several applications formulated 
with the LS scheme. Finally, high-performance of the Linear Steklov 
method  have been analyzed in diverse problems for which other methods 
have failed.



% %
% %********************************************************************************************
% %				 Bibliography
% %********************************************************************************************
% 
% 	\pagebreak
% 	\section*{\refname}
\begin{thebibliography}{26}
\providecommand{\natexlab}[1]{#1}
\providecommand{\url}[1]{\texttt{#1}}
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{doi: #1}\else
  \providecommand{\doi}{doi: \begingroup \urlstyle{rm}\Url}\fi

  
  \bibitem[Cruz et~al.(2012)Cruz, Chinesta, and R\'{e}gnier]{Cruz2012}
C.~Cruz, F.~Chinesta, G.~R\'{e}gnier.
\newblock Review on the brownian dynamics simulation of bead-rod-spring models
  encountered in computational rheology,
\newblock Arch. Comput. Methods Eng. 19 (2012) 227--259.

\bibitem[Dalal et~al.(2008)Dalal, Greenhalgh, and Mao]{Dalal2008}
N. Dalal, D. Greenhalgh,  X. Mao,
\newblock A stochastic model for internal HIV dynamics
\newblock J. Math. Anal. Appl.
  341 (2008) 1084--1101.

\bibitem[D\'{\i}az-Infante and Jerez(2015)]{Diaz-Infante2015}
S. D\'{\i}az-Infante, S. Jerez,
\newblock Convergence and asymptotic stability of the explicit Steklov method
  for stochastic differential equations,
\newblock J. Comput. Appl. Math. 291 (2016) 36--47.

\bibitem[Fine and Kass(1966)]{FineAIandKass1966}
A. I. Fine,  S. Kass,
\newblock Indeterminate forms for multi-place functions,
\newblock Ann. Polon. Math. 18 (1965) 59--64.

\bibitem[{Gao et~al.(2002)Gao, Tung y Rao}]{Gao2002}
\bibinfo{author}{J.B. Gao}, \bibinfo{author}{W. Tung},
  \bibinfo{author}{N. Rao}, 
\newblock \bibinfo{title}{Noise-induced hopf-bifurcation-type sequence and
  transition to chaos in the lorenz equations}.
\newblock \bibinfo{journal}{Phys. Rev. Lett.} \bibinfo{volume}{89} (2002)
  \bibinfo{pages}{254101}.

\bibitem[Giles(2008)]{Giles2008}
M. B. Giles,
\newblock Multilevel monte carlo path simulation,
\newblock Oper. Res. 56 (2008) 607--617.

\bibitem[Glasserman(2004)]{Glasserman2004}
P.~Glasserman,
\newblock Monte Carlo Methods in Financial Engineering,
\newblock Applications of mathematics: stochastic modelling and applied
  probability, Springer, 2004.
  

\bibitem[Higham et~al.(2002)Higham, Mao, and Stuart]{Higham2002b}
D. J. Higham, X. Mao,  A. M. Stuart,
\newblock Strong convergence of euler-type methods for nonlinear stochastic
  differential equations,
\newblock  SIAM J. Numer. Anal. 40  (2002)  1041--1063.


\bibitem[Hutzenthaler and Jentzen(2015)]{Hutzenthaler2015}
M. Hutzenthaler, A. Jentzen, 
\newblock Numerical approximations of stochastic differential equations with
  non-globally lipschitz continuous coefficients,
\newblock Mem. Amer. Math. Soc. 236 (2015).


\bibitem[Hutzenthaler et~al.(2011)Hutzenthaler, Jentzen, and
  Kloeden]{Hutzenthaler2009}
M. Hutzenthaler, A. Jentzen,  P. E. Kloeden,
\newblock Strong and weak divergence in finite time of euler's method for
  stochastic differential equations with non-globally lipschitz continuous
  coefficients,
\newblock Proc. R. Soc. Lond. Ser. A Math. Phys. Eng. Sci. 467 (2011) 1563--1576.


\bibitem[Hutzenthaler et~al.(2012{\natexlab{a}})Hutzenthaler, Jentzen, and
  Kloeden]{Hutzenthaler2012a}
M. Hutzenthaler, A. Jentzen,  P. E. Kloeden,
\newblock Strong convergence of an explicit numerical method for sdes with
  nonglobally lipschitz continuous coefficients.
\newblock Ann. Appl. Probab. 22 (2013) 611--1641.


\bibitem[Hutzenthaler et~al.(2013)Hutzenthaler, Jentzen, and
  Kloeden]{Hutzenthaler2012b}
M. Hutzenthaler, A. Jentzen,  P. E. Kloeden,
\newblock Divergence of the multilevel monte carlo euler method for nonlinear
  stochastic differential equations.
\newblock Ann. Appl. Probab. 23 (2013)  1913--1966.

\bibitem[{Kloeden y Platen(1992)}]{Kloeden1992}
P.E. Kloeden, E. Platen,
\newblock Numerical Solution of Stochastic Differential Equations
\newblock Springer-Verlag, 1992. 


\bibitem[Lawlor(2012)]{Lawlor2012}
G. R. Lawlor,
\newblock A l'hospital's rule for multivariable functions,
\newblock arXiv preprint (2012) arXiv:1209.0363.

\bibitem[Liu and Mao(2013)]{Liu2013a}
W. Liu, X. Mao,
\newblock Strong convergence of the stopped euler-maruyama method for nonlinear
  stochastic differential equations,
\newblock Appl. Math. Comput. 223 (2013) 389--400.

\bibitem[Mao(2007)]{Mao2007}
X. Mao,
\newblock Stochastic Differential Equations and Application,
\newblock Horwood Pub., 2007.

\bibitem[Mao(2015)]{Mao2015}
X. Mao,
\newblock The truncated euler-maruyama method for stochastic differential
  equations,
\newblock J. Comput. Appl. Math. 290 (2015) 370--384.

\bibitem[Mao et~al.(2002)Mao, Marion, and Renshaw]{Mao2002}
X. Mao, Gl. Marion,  E. Renshaw,
\newblock Environmental brownian noise suppresses explosions in population
  dynamics,
\newblock Stochastic Processes and their Applications, 97 (2002) 95--110.

\bibitem[Mao et~al.(2003)Mao, Sabanis, and Renshaw]{Mao2003}
X. Mao, S. Sabanis, E. Renshaw.
\newblock Asymptotic behaviour of the stochastic lotka-volterra model,
\newblock Journal of Mathematical Analysis and Applications
  287 (2003) 141--156, 2003.


\bibitem[Mao and Szpruch(2013)]{Mao2013}
X. Mao, L. Szpruch,
\newblock Strong convergence and stability of implicit numerical methods for
  stochastic differential equations with non-globally lipschitz continuous
  coefficients,
\newblock J. Comput. Appl. Math.
  238 (2013) 14--28.
  
 

\bibitem[Sabanis(2015)]{Sabanis2015}
S. Sabanis,
\newblock Euler approximations with varying coefficients : the case of
  superlinearly growing diffusion coefficients,
\newblock to appear in Ann. Appl. Probab.

\bibitem[{Schenk-Hopp\'{e}(1996)}]{Schenk-Hoppe1996b}
\bibinfo{author}{K. R. Schenk-Hopp\'{e}}, 
\newblock \bibinfo{title}{Stochastic hopf bifurcation: An example},
\newblock \bibinfo{journal}{International Journal of Non-Linear Mechanics}
  \bibinfo{volume}{31} (1996) \bibinfo{pages}{685--692}.

\bibitem[{Tornatore et~al.(2005)Tornatore, Buccellato y Vetro}]{Tornatore2005}
\bibinfo{author}{E. Tornatore}, \bibinfo{author}{Buccellato, S.M.},
  \bibinfo{author}{P. Vetro}, 
\newblock \bibinfo{title}{Stability of a stochastic \{SIR\} system}.
\newblock \bibinfo{journal}{Physica A: Statistical Mechanics and its
  Applications}  \bibinfo{volume}{354} (2005) \bibinfo{pages}{111 -- 126}.

\bibitem[Tretyakov and Zhang(2013{\natexlab{a}})]{Tretyakov2013}
M. V. Tretyakov, Z. Zhang.
\newblock A fundamental mean-square convergence theorem for sdes with locally
  lipschitz coefficients and its applications,
\newblock SIAM J. Numer. Anal. 51 (2013) 3135--3162.



\bibitem[Wang and Gan(2013)]{Wang2011}
X. Wang,  S. Gan.
\newblock The tamed milstein method for commutative stochastic differential
  equations with non-globally lipschitz continuous coefficients,
\newblock J. Difference Equ. Appl. 19 (2013) 466--490.


\bibitem[Zong et~al.(2014)Zong, Wu, and Huang]{Zong2014}
X. Zong, F. Wu, Ch. Huang,
\newblock Convergence and stability of the semi-tamed euler scheme for
  stochastic differential equations with non-lipschitz continuous coefficients.
\newblock Appl. Math. Comput. 228
  (2014)  240--250.


\end{thebibliography}
