	In this section we show that the explicit Linear Steklov method 
\cref{eqn:SSLSM1,eqn:SSLSM2} converges  with a standard order of one-half. For that,
we use a similar procedure  as in  \cite{Higham2002b}. In addition 
to \Cref{ass:OSLC,ass:ajBound,ass:HypThmSingularities} we also require the following.
 
 \begin{hypothesis}\label[hypothesis]{ass:PolynomialGrowth}
 	There exist constants $L_f, D\in \R$ and $q \in \Z^+$ such that $\forall u,v \in \R^d$
 	\begin{align}
 	\innerprod{u-v}{f(u)-f(v)}
 	&\leq L_f|u-v|^2, \\
 	|f(u) - f(v)|^2 
 	&\leq 
 	D(1 + |u|^q +|v|^q) |u-v|^2.
 	\end{align}
 \end{hypothesis}
 
 \begin{hypothesis}\label[hypothesis]{ass:MomentBounds}
 	The SDE \eqref{eqn:SDE1}  the EM solution and its continuous extension satisfy
 	\begin{equation}
 	\EX{
 		\sup_{0\leq t\leq T}
 		|y(t)|^p	
 	}, \quad
 	\EX{
 		\sup_{0\leq t\leq T}
 		|Y(t)|^p	
 	}, \quad
 	\EX{
 		\sup_{0\leq t\leq T}
 		|\overline{Y}(t)|^p	
 	} < \infty, \qquad \forall p\geq 1.
 	\end{equation}
 \end{hypothesis}

 \begin{thm}\label{thm:EulerConvergenceRateHMS}[{\citet[Thm 4.4]{Higham2002b}}]
 	Under \Crefrange{ass:ajBound}{ass:PolynomialGrowth} the EM solution with continuous extension $\overline{X}$
 	satisfies
 	\begin{equation}
 	\EX{
 		\sup_{0\leq t \leq T}
 		|\overline{Y}(t)- y(t)|^2
 	} = \mathcal{O}(h^2).
 	\end{equation}
 \end{thm}
  
\begin{lem}
	Under \Cref{ass:PolynomialGrowth,ass:MomentBounds} and sufficiently small $h$, there exist
	constants $D'\in \R$ and $q'\in \Z$ such that for all $u,v\in \R^d$
	\begin{align}
		|
			\varphi_{f_h}(u)
			-\varphi_{f_h}(v)
		|^2 
		&\leq
			D'
			\left(
				1 +|u|^{q'} +|v|^{q'}
			\right)
			|u-v|^2, \\
		%
		|
			 f(u) -\varphi_{f_h}(u)
		|^2 
		&\leq
			D'
			\left(
				1 +|u|^{q'} 
				\right)
			h^2, \\
		%
		|
			g(u) -g_h(u)
		|^2 				 
		&\leq
			D'
			\left(
				1 +|u|^{q'} 
			\right)
			h^2 . \label{eqn:ghPolyGrowth}
	\end{align}
\end{lem}

\begin{pf}
	From inequality \eqref{eqn:PhifhFbound}, we have
	\begin{equation*}
		|\varphi_{f_h}(u) - \varphi_{f_h}(v)|^2
		\leq
			(2 + L_{\Phi}) |f(u) - f(v)|^2 
			\leq
				(2 + L_{\Phi}) D (1 + |u|^q +|v|^q). 
	\end{equation*}
	Moreover, if $u \in E_j$ then $\varphi_{f_h}(u) = f^{(j)}(u)$. On the other hand,  if $u\in E_j^c$ then
	$$
		|f(u) - \varphi_{f_h}(u)|^2
		=
		\sum_{j=1}^d
			|1-\Phi(h,a_j)(u)|^2 |f^{(j)}(u)|^2,	
	$$
	 By the L'H\^{o}pital 
	theorem, we get
	\begin{align*}
		\lim_{h \to 0} |1-\Phi(h,a_j)(u)| 
			&= \left|
				1-\lim_{h\to 0} \frac{e^{h a_j(u)}-1}{h a_j(u)}
			\right|			
			\leq 
				\left|
					1-\lim_{h\to 0} e^{h L_a}
				\right|=0.			
	\end{align*}
	Thus, there is a sufficiently small $h>0$  such that
	$|1-\Phi_j(u)|<C h$ for all $u\in E_j^c$ and
	$$
		|f(u) - \varphi_{f_h}(u)|^2
		\leq
		Ch^2 |f(u)|^2
		\leq D'(1+|u|^q)h^2,	
	$$
	as we require. Given that $g_h(u)=g(F_h(u))$ from 
	theorem \ref{lem:PhiFhProp} we get
	\begin{equation*}
		|g(u) - g_h(u)|^2 
		\leq
			L_g |u - u +h \varphi{f_h}(u)|^2 
		\leq 
			2(1+L_{\Phi})h^2 |f(u)|^2
		\leq
			2(1+L_{\Phi}) D(1+|u|^q) h^2. 
	\end{equation*}
	\qed
\end{pf}
%
\begin{lem}\label{lem:yhyOh}
	Assume \Cref{ass:PolynomialGrowth,ass:MomentBounds} hold then the solution $y_h(t)$ of 
	the modified SDE \eqref{eqn:PerturbedHighamSDE}
	satisfies
	\begin{equation}
		\EX{
			\sup_{0\leq t \leq T}
			|y_h(t) - y(t)|^2	
		} = \mathcal{O}(h^2).
	\end{equation}	
\end{lem}
\begin{pf}
	We define $e(t):= y(t)-y_h(t)$ where
	\begin{eqnarray*}
		y(t) &=& y_0 + \int_{0}^t f(y(s))ds + \int_{0}^t g(y(s))dW(s),  \nonumber\\
		y_h(t) &=& y_0 + \int_{0}^t \varphi_{f_h}(y_h(s))ds + \int_{0}^t 
		g_h(y_h(s))dW(s).\nonumber
	\end{eqnarray*}
	Using It\^{o}'s formula over the function $V(t,x,y) = |x-y|^2$ for all  $x,y\in \R^d$, we obtain 
$$
		d e(t) = 
		\left(
			f(y(t)) - \varphi_{f_h}(y(t)) dt
		\right)
		+
		\left(
			g(y(t)) - g_h(y_h(t))
		\right) dW(t),
	$$
	Thus,
	\begin{align} \label{eqn:IntErrToBound}
		|e(t)|^2 
		&=
			2 \underbrace{\int_{0}^t
				\innerprod{e(s)}{f(y(s))-\varphi_{f_h}(y_h(s))} ds }_{:=I_1}
			+
			\underbrace{\int_{0}^t
				|g(y(s)) - g_h(y_h(s))|^2 ds }_{:=I_2}\notag\\
		&+
			2 \underbrace{\int_{0}^t
				\innerprod{e(s)}{\left[ g(y(s))-g_h(y_h(s)) \right] dW(s)}}_{:=I_3}.	\end{align}
	Now we proceed to bound each integral of inequality \eqref{eqn:IntErrToBound}. 
	By \Cref{ass:PolynomialGrowth} and the Young inequality, we get
	\begin{align*}
		I_1(t) 
		&\leq
			2\int_0^t
				\innerprod{y(s) - y_h(s)}{f(y(s))-f(y_h(s))} ds
			+
			 \int_0^t
				 \innerprod{y(s) - y_h(s)}{f(y_h(s))-\varphi_{f}(y_h(s))} ds \notag\\
%	
		&\leq
			3\int_0^t
				|y(s) - y_h(s)|^2ds
			+ D' h^2 
			\int_0^t
				1 + |y_h(s)|^{q'} ds.
	\end{align*}
	Since $y_h(t)$  the has bonded moments, there exists a universal constant $L$ which does not depends on $h$ 
	such that
	\begin{equation}\label{eqn:I1Bound} 
		 \EX{
			 I_1(s)	
		 }
		 \leq
			 L\int_{0}^t
				\m{|e(s)|^2} ds
		+ L h^2.
	 \end{equation}
	Using  \Cref{ass:OSLC,ass:PolynomialGrowth} it is followed
	\begin{align*}
		I_2(t) 
		&\leq
			2 L_g 
			\int_{0}^t
				|y(s) - y_h(s)|^2 ds
			+
			2D'h^2
			\int_0^t
				1 + |y_h(s)|^q ds, 	 
	\end{align*}
	thus
	\begin{equation} \label{t5}
		\EX{
			I_2(s)	
		}
		\leq
		L\int_{0}^t
		\m{|e(s)|^2} ds
		+ L h^2.
	\end{equation}
	Note that $\EX{ I_3(t)} \leq \EX{ 
				\sup_{0\leq s \leq t}
				|I_3(s)|
			}$.
	From the Burkholder-Davis-Gaundy inequality, \Cref{ass:OSLC,ass:PolynomialGrowth} and 
	as $y_h(t)$ has bounded moments, we obtain
	\begin{align}
		\EX{ 
			\sup_{0\leq s \leq t}
			|I_3(s)|
		}
		%
		&\leq
		2^4 
		\EX{
			\sup_{0 \leq s \leq t}
			|e(s)|^2
			\int_{0}^t
				|g(y(s))-g_h(y(s))|^2 ds
		}^{1/2} \notag \\
		&\leq
		2^4 
		\EX{
			\frac{1}{2 \cdot 2^9}
			\left(
				\sup_{0\leq s \leq t}
				|e(s)|^2
			\right)			
			+
			\frac{2^9}{2}
			\left(
				\int_{0}^t
					|g(y(s)) - g_h(y_h(s))|^2 ds
			\right)^2
		}
		\notag \\
		&\leq
			2 L_g
			\EX{
				\int_{0}^t
					|y(s) - y_h(s)|^2 ds		
				} 
			+D'Th^2 
			+
			D'Th^2
			\int_{0}^t
				\m{|y_h(s)|^{q'}} ds 	
		\notag \\
		&\leq
			L
			\int_{0}^t
				\m |e(s)|^2 ds
			+L h^2. \label{eqn:I3Bound}
	\end{align}
	Substituting inequalities \eqref{eqn:I1Bound}, \eqref{t5} and \eqref{eqn:I3Bound} 
	on equation \eqref{eqn:IntErrToBound}, we deduce that
	\begin{equation*}
		\EX{
			\sup_{0\leq s \leq t}	
			|e(t)|^2
		}
		\leq
			L \int_0^t
				\m |e(s)|^2 ds
			+
			L h^2 
		\leq		
			L \int_{0}^t
				\EX{
					\sup_{0\leq r \leq s}
					|e(s)|^2	
				}ds
			+Lh^2.		
	\end{equation*}
	By the Gronwall inequality, we conclude that
	\begin{equation*}
		\EX{
			\sup_{0 \leq t \leq T} 	
			|e(t)|^2
		}
		\leq
			L  \exp(LT) h^2 \leq C h^2. 
	\end{equation*} 	\qed
		
\end{pf}

	We  can now obtain the convergence rate of the explicit Linear Steklov method.

\begin{thm}
	Under \Crefrange{ass:OSLC}{ass:PolynomialGrowth} and consider the explicit \SM method 
	\eqref{eqn:SolutionFunctions} for the SDE \eqref{eqn:SDE1}.
	Then there exists a continuous-time extension $\overline{Y}(t)$ of the 
	LS numerical approximation for which
	\begin{equation} \label{orden}
		\EX{
			\sup_{0 \leq t \leq T}
			|\overline{Y}(t) - y(t)|^2	
		} = \mathcal{O}(h).	
	\end{equation}
\end{thm}
\begin{pf} Using bound  \eqref{eqn:AfterTriangle} then by  lemma \ref{lem:yhyOh} and since
 the LS continuous-time extension \eqref{eqn:SSLSContinuousExtension} is equivalent to the EM continuous-time extension 
 \eqref{eqn:EMContinuousExtension}, 
 we can use \Cref{thm:EulerConvergenceRateHMS} and conclude that the \SM has order one-half. \qed
\end{pf}
