

	Applications of Monte Carlo simulations \cite{Glasserman2004,Giles2008} and  Brownian Dynamics \cite{Cruz2012}
 require  fast numerical methods with low computational cost, thus excluding the use of 
 implicit schemes in the majority of cases. The Euler-Maruyama (EM) method is the most popular in such  
 simulations due to its simple algebraic structure, a cheap computational cost and an acceptable convergence rate 
 under global Lipschitz conditions.  However, if the drift or diffusion coefficients of stochastic 
 differential equations (SDEs) are non-globally Lipschitz functions with a super-linear growth, then the Euler-Maruyama approximation 
 diverges  in the mean square sense \cite{Hutzenthaler2009, Hutzenthaler2012b}. 
In most applications, the coefficients of the stochastic  models in finances, biology or physics 
have super-linear growth and locally Lipschitz coefficients. Therefore recent research has been 
focused on modifying the Euler-Maruyama method to obtain strong convergence  under these conditions keeping
 its simple structure and  its low computational cost. In the last years, 
 several methods have been developed in this direction:  the family of  Tamed schemes
\cite{Hutzenthaler2012a, Wang2011, Zong2014,Hutzenthaler2015,Sabanis2015}, 
a special type of balanced method \cite{Tretyakov2013},  the stopped scheme \cite{Liu2013a} and 
a truncated Euler method  \cite{Mao2015}.  In these works, the strong convergence of the proposed method
is proved using the theory developed by Higham, Stuart and 
Mao in \cite{Higham2002b} or by means of  the new approach given by  Hutzenthaler and Jentzen in \cite{Hutzenthaler2015}.
Both techniques obtain the property of  strong convergence by proving boundedness moments of the numerical and 
analytical solution of the underlying SDE. In spite of the recent work in this subject,  it is still necessary
to get more accurate numerical methods for SDE under super-linear growth and 
non-globally Lipschitz coefficients.

In this paper, we develop an explicit method based on a linear version  of the Steklov method proposed 
in  \cite{Diaz-Infante2015}  for the  vector It\^o stochastic differential equation:
\begin{equation}\label{eqn:SDE1}
	dy(t)
	 =f(y(t))dt + g(y(t))dW(t), \quad 0\leq t\leq T,
	\quad y(0)=y_0,
\end{equation}
where $(f^{(1)},\dots, f^{(d)}):\R^d \to \R^d$ is one sided Lipschitz and 
$g = (g^{(j,i)})_{j\in \{1,\dots,d\}, i\in\{1,\dots, m\}}:\R^d \to \R^{d\times m}$ is global Lipschitz. 
Also we assume 
that  each component function $f^{(j)}$  can be written of the form
\begin{equation}\label{eqn:AlternativeConstruction}
	f^{(j)}(x) = a_j(x) x^{(j)} + b_j (x^{(-j)}), 
\end{equation}
where $a_j$ and	$b_{j}$ are two scalar 	functions in  $\R^d$ 
and $x^{(-j)} = \left( x^{(1)},\dots,x^{(j-1)},x^{(j+1)},\dots x^{(d)}\right)$. 
The paper is organized as follows: In section 2, we give known results that are essential
for our purposes. In section 3, we construct the new explicit method and prove  
 the always existence of a succession of the Linear Steklov  approximation as well as 
  local Lipschitz conditions for its coefficients.  
  In section 4, we prove the strong convergence of the LS method 
with one-half order using the Higham, Stuart and 
Mao (HSM) technique and in section 5, its  convergence rate is obtained. 
In section 6, we analyze numerically  the accuracy and efficiency of the proposed method 
applied to stochastic  differential equations with super-linear growth and locally Lipschitz coefficients. 
Finally we give some conclusions.

