\chapter*{Abstract\markboth{Abstract}{Abstract}}\label{ch:Abstract}
	\addcontentsline{toc}{chapter}{Abstract}
	
	We propose a new way to construct numerical methods for stochastic differential equations (SDEs) via Steklov means. 
	Here we present two schemes which evidence the properties of this new approach. First, we construct a scheme 
	for scalar SDEs and prove its convergence and stability under standard globally Lipschitz and linear growth 
	conditions. Moreover, we give sufficient conditions for the nonlinear asymptotic stability in both multiplicative 
	and additive cases. Finally, we showed the behavior of the explicit Steklov method for problems with stringent 
	stability requirements as the logistic stochastic equation and the Langevin equation in Brownian dynamics.
	In all these studies, we established that the Steklov method is an accurate scheme for large time scales 
	simulation. The second scheme extends the previous method towards a multidimensional set up and coefficient with 
	locally Lipschitz and monotone grow conditions for the coefficients. This method is constructed on the basis that 
	the drift function can be rewritten in the linearized form. Moreover, strong order one-half convergence has been 
	proved for our explicit linear method and we have presented several applications formulated with the \SM scheme. 
	Also, we present numerical evidence that confirms our theoretical results and suggests an extension to super-linear 
	growth diffusions. Finally, high-performance of the Linear Steklov method have been analyzed in diverse problems 
	for which other methods have failed. 
	
	
	
