\chapter*{
	Thesis Details
		\markboth{Thesis Details}{Thesis Details}
	}
	\addcontentsline{toc}{chapter}{Thesis Details}
%this is a mandatory page. You can see more at http://www.phd.teknat.aau.dk/intranet/templates/
\begin{tabularx}{\textwidth}{@{}>{\bfseries}l X@{}}
	Title:			& Steklov Methods for non Linear Stochastic Differential
					Equations.\\
	Ph.D. Student:	& Sa\'ul D\'iaz Infante Velasco.\\
	Supervisor:		& Prof.\ Silvia Jerez Galiano, CIMAT A.C.\\
\end{tabularx}
\vspace{\baselineskip}

% list the papers included in this thesis
\noindent The main body of this thesis consist of the following papers.
\begin{itemize}
  \item[{[\ref{paper:paperA}]}] Sa\'ul D\'iaz-Infante, Silvia Jerez
  "Convergence and asymptotic stability  of  the explicit Steklov method for stochastic differential 
	equations,'' \emph{Journal of Computational and Applied Mathematics}\\ 
	DOI: 10.1016/j.cam.2015.01.016 14-FEB-2015
	vol.~291, pp. 36-47, 2015.
  \item[{[\ref{paper:paperB}]}] Sa\'ul D\'iaz-Infante, Silvia Jerez,
	The Linear Steklov Method for SDEs with non-globally Lipschitz
	Coefficients: Strong convergence and simulation. Paper submitted at
	\emph{Journal of Computational and Applied Mathematics.}
	
\end{itemize}
\noindent This thesis has been submitted for partial fulfillment of the PhD degree. The thesis is based 
on the submitted or published scientific papers which are listed above. Parts of the papers are used directly or 
indirectly in the extended summary of the thesis. As part of the assessment, co-author statements have been made 
available to the Ph. D. committee and are also available at the Faculty. 